---
title: "Basic Process for Final project (R programming)"
author: "Khash"
date: "4/9/2022"
output: html_document
---

```{r setup,  message = FALSE}
library(XML)
library(tm)
library(wordcloud)
library(tidytext)
```


This is over all series of the functions I will use in package for the final project. Notice that functions are still being developed and at the end, I may add certain features which are not still present in this document.

Also, some functions may not be working properly at this moment.

For this document I have condicted a test run of all functions which will used to create my final function for the final project.
```{r cars}

#Different ways to read the speech 
#in all these cases inputText.txt is locally saved on my computer
textAnalysisFunction<- function(input){
#use scan to read the file
inputText <- scan("C:\\Users\\wecan\\OneDrive\\Documents\\Final project for R ( text analysis)\\sampleone.txt", character(0),sep = ".")
inputText
```

Developing word corpus and turning it into tdm:
```{r}

words.vec <- VectorSource(inputText)
words.corpus <- Corpus(words.vec)
words.corpus
words.corpus <- tm_map(words.corpus, content_transformer(tolower))
words.corpus <- tm_map(words.corpus, removePunctuation)
words.corpus <- tm_map(words.corpus, removeNumbers)
words.corpus <- tm_map(words.corpus, removeWords, stopwords("english"))
tdm <- TermDocumentMatrix(words.corpus)
tdm
inspect(tdm)
m <- as.matrix(tdm)
wordCounts <- rowSums(m)
wordCounts <- sort(wordCounts, decreasing=TRUE)
head(wordCounts)
```

Pert1 : Making a word cloud 

```{r}

cloudFrame <- data.frame(word = names(wordCounts), freq=wordCounts)
wordcloud(cloudFrame$word, cloudFrame$freq)
wordcloud(names(wordCounts), wordCounts, min.freq=2, max.words=50, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

Part 2: Positive and negative words 

```{r}
#after downloading our dictionary, we should have two text file one for positive words and the other 
#for negative words


get_sentiments("bing")
#then in console, select 1

pos <- "C:\\Users\\wecan\\OneDrive\\Documents\\bing\\positive-words.txt"
neg <- "C:\\Users\\wecan\\OneDrive\\Documents\\bing\\negative-words.txt"

#now we have read both the positive and the negative words, we should put them in vectors
p <- scan(pos, character(0),sep = "\n")
n <- scan(neg, character(0),sep = "\n")

#one we print out the head of both vectors, we notice that roughly the first 30 elements of our 
#vectors are infact extra information which are not useful for our code, we are just going to take them
#out
head(p, 50)
head(n, 50)

p <- p[-1:-34]
n <- n[-1:-34]
head(p, 10)
head(n, 10)

#totalWords is the sum of the all the terms used in inputText spa.txt in the order of their frequency
totalWords <- sum(wordCounts)

#words is the actual terms in the speech which are aquired by using the names function
words <- names(wordCounts)

#now we use the match function to determine how many of the words used in inputText.txt are are found
#within the positive words dictionary. the ones that there are no match for (nuetral words for instance)
#are simply designated to be 0

matched <- match(words, p, nomatch = 0) 

#Now we have a vector of all positive words from our dictionary that are matched with positive words
#with our inputText.txt speech

#mCounts finds which words in matched vector are not 0 (in other words which words were matched from 
#our dictionary to our speech)
#mCounts vector therefore includes only words that were matched

mCounts <- wordCounts[which(matched != 0)]


#now let's see how many positive words are there in total
mWords <- names(mCounts)
nPos <- sum(mCounts)


# we will do the same for our negative words:
matched <- match(words, n, nomatch = 0)
nCounts <- wordCounts[which(matched != 0)]
nNeg <- sum(nCounts)
nWords <- names(nCounts)


#here we modified the totalWords to be the length of all words in the speech
#"words" was the name of all the terms in wordCounts.
totalWords <- length(words)

#Now let's compare the ratio of the all positive words used in the speech against all the words in
#the pseech as well as the ratio of all negative words used in the speech against all the words in 
#the speech
ratioPos <- nPos/totalWords
ratioPos
ratioNeg <- nNeg/totalWords
ratioNeg

ratioPos <- nPos/totalWords
  ratioPos<- ratioPos*100
  ratioNeg <- nNeg/totalWords
  ratioNeg<- ratioNeg*100
  
  mylist<- list("Percent of Positive words"=ratioPos,"Percent of Negative words"=ratioNeg,"Black and White Word-Cloud"=couldbw,"Colorful Word-Cloud"=couldColor)
  return(mylist)
  }
``` 

